Out-of-Sample Comparisons of Overfit Models

### 2014-03-27 paper.tex
Revise empirical write-up
This commit makes several minor changes to the empirical section.

This section presents two simulations that investigate the accuracy of
our theory in small samples.%
\footnote{Simulations were conducted in R \citep{Rde:10} using the
  MASS \citep{VeR:02}, Matrix \citep{BM:13}, rlecuyer \citep{SR:12},
  and RSQLite \citep{Jam:10} packages. Graphs were produced in R using
  Lattice \citep{Sar:10} and tikzDevice \citep{ShB:11:0.6.1} as well
  as the TikZ and PGF LaTeX packages \citep{Tan:10}} %
The first looks at the asymptotic normality of the DMW statistic
centered on either $\E_R \oosA$ or $\E_T \oosB$.  The previous
section's results imply that centering on the first should give an
approximately normal statistic and centering on the second should give
a normal statistic when $P$ is small relative to $T$.  The second
simulation looks at the size and power of several statistics when
conducting inference about the difference in the models'
generalization error.  For all of the simulations, we look at
fixed-window OOS tests to speed up computation time.

@@

The Monte Carlo experiment is intentionally very simple so that we can
isolate the influence of the models' complexity.  In particular, we do
not include some features that are common in forecasting
environments---serial dependence, heteroskedasticity, and complicated
DGPs.  We simulate data for both studies from the equation
\begin{equation}\label{eq:6}
  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
  \quad t=1,\dots,T.
\end{equation}
The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
independent Standard Normal.  The benchmark model is
\begin{equation}
  \label{eq:1}
  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
\end{equation}
and the alternative model is the DGP \eqref{eq:6}.  We let
$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
in its intended application as well as for more parsimonious models.
We let $T$ equal 100, 250, 500, or 1000.  We also vary $\theta$, and do
so giving the benchmark and the alternative model comparable weight in
predicting $y_t$.  Specifically, we set
\begin{equation*}
  \theta_j =
\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
\end{equation*}
with $c$ equal to zero or one.  When $c$ is one, we're more likely to
draw values of $X$ and $Y$ that make the estimated larger model more
accurate than the benchmark, and when $c$ is zero we're unlikely to
draw such values of $X$ and $Y$.  For all of the studies, $L(x) =
x^2$.

The first set of simulations study how well the theory in
Section~\ref{sec:oostheory} works in practice.  For each draw of $X$
and $Y$, we construct a one-sided OOS interval of the
form
\begin{equation*}
  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
\end{equation*}
for $P$ set to every 10th value between 1 and $2T/3$.  We calculate
the percentage of these intervals that contain $\E_R \oosA$ and that
contain $\E_T \oosB$.  Since the data are i.i.d., both of these
quantities are easy to calculate:
\begin{equation*}
  E_R \oosA = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iR} - \theta_i)^2 +
  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iR} -
  \theta_i)^2
\end{equation*}
and
\begin{equation*}
  E_T \oosB = \Bigg[\sum_{i=1}^{K_1} (\tilde{\theta}_{iT} - \theta_i)^2 +
  \sum_{i=K_1+1}^{K_2}\theta_i^2\Bigg] - \sum_{i=1}^{K_2} (\hat{\theta}_{iT} -
  \theta_i)^2
\end{equation*}
where $\tilde{\theta}$ indicates that the coefficient is estimated
using only the regressors in the benchmark model and $\hat{\theta}$
the full model.  We draw 2000 samples for each combination of the
design parameters.

The second simulation looks at the size and power of the test
statistics when conducting inference about the models' generalization
error.  The null hypothesis we test is
\begin{equation*}
  H_0:\quad E_T \oosB \leq 0,
\end{equation*}
We look at four different statistics---the full-sample $F$-test, the
DMW $t$-test, the
OOS $t$-test using McCracken's (2007)
critical values,%
\footnote{These critical values are not published for
  $K_2-K_1>10$, so we do not report them for $K_2 = T/10$.} %
and Clark and West's (2006, 2007) Gaussian out-of-sample
statistic.%
\footnote{Clark and West (2006, 2007) derive their statistic
using the rolling window estimation scheme.  Here we use the same
statistic, but with a fixed window scheme.} %
For the $F$-test, we simply test whether the coefficients on the larger
model are nonzero.  For the out-of-sample tests, we conduct a
one-sided test of out-of-sample performance for every 10th value of
$P$ as before.

To estimate each test's size for the null hypothesis, we draw
samples from the DGP and discard those for which the null does
not hold, until we have 2000 for each choice of the design parameters.
The estimated size is the fraction of those samples in which the test
statistic rejects.

@@

We discuss results for the confidence intervals first.
Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
coverage probability of these intervals as a function of $P$ for each
combination of $T$, $K_1$ and $K_2$, and $c$.  The gray horizontal
line shows the intervals' nominal coverage probability.  Each panel
displays the coverage for a different choice of interval, centering
term ($\E_R \oosA$ or $\E_T \oosB$) and combination of design
parameters.

Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
actual coverage is very close to the nominal coverage except when $P$
is very small.  The poor behavior for small $P$ is unsurprising, as it
simply means that the CLT is a poor approximation when the test
sample is small.  The intervals' good coverage holds even for the
parsimonious models ($K_1=1$ and $K_2= 3$) which our theory does not
necessarily apply to.

Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
rows 2, 4, 6, and 8---the overfit models---the coverage is near
nominal coverage for moderately small values of $P$.  As $P$ increases
to $2T/3$, the coverage increases to 1.  With the parsimonious model,
the coverage is near nominal coverage for all $P$ for the one-sided
interval with $c=1$, but only for moderately small $P$ when $c=0$.

The behavior for $K_2 = T/10$ is exactly what our theory predicts.
When $P^2/T$ is small, the coverage is near nominal levels.  The
behavior as $P$ increases, combined with the results for $\E_R
\oosA$, indicate that $\E_T \oosB \geq E_R \oosA$ in general.
Since
\[E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA), \] and the
interval is approximately centered at $\E_R \oosA$, the difference
$\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive quantity when
$P^2/T$ is not near zero, increasing the coverage of the one-sided
interval.

We next present the size simulations,
Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests,
the conditional rejection probability is plotted for each combination
of $T$, $K_1$, $K_2$, and $c$ as a function of $P$.  The $F$-test does
not depend on $P$, so a single value is presented for each
combination.

We'll look at the $F$-test first.  To make comparisons easier, the size
is displayed as a dot plot in Figure~\ref{fig:ftest}.  Different
panels display a different combination of $K_1$, $K_2$, and $T$, and
each individual plot shows the empirical size for each choice of $c$.
We see immediately that the actual and nominal size are essentially
equal for $c = 0$, which is unsurprising.  For $c = 0$, the $F$-test is
exact; moreover, the larger model will almost always be less accurate
than the smaller one, so conditioning on $\E_T \oosB \leq 0$ is
almost unrestrictive.  When $c$ increases, though, the $F$-test
overrejects badly---rejecting at roughly 50\% when $c = 1$ for the
parsimonious model and from 70\% to 100\% for the overfit model.  As
our discussion in Section~\ref{sec:insample} predicts, the rejection
probability increases with $T$ for the overfit model but does not
depend on $T$ for the small model.

Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
$t$-test.  Again, different panels display results for different
combinations of the design parameters.  Each graph plots the rejection
probability against $P/T$.  For $K/T=10$, the rejection probability
falls as $P/T$ increases, from near nominal size when $P/T$ is small
to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
falls faster when $T$ is large, as our theory predicts.  When $K=3$,
the rejection probability stays closer to nominal size, but falls with
$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
rises with $P/T$ for $c=1$, overrejecting by about 10pp when
$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
probability is about 5\%; the other simulations are much closer).

@@

Results using \citepos{Mcc:07} critical values are
presented in Figure~\ref{fig:mccracken} and are similar to those using
Clark and West's test.  For $c=0$ the rejection probability is nearly
the test's nominal size.  For $c=1$, the rejection probability
increases with $P/T$, from close to the nominal size when $P/T$ is
small to over 25\% when $P/T = 2/3$.  Note that all of the simulations
use the parsimonious model.  McCracken's statistic overrejects here
by slightly less than Clark and West's, but still by a substantial
amount.

Since the DMW test tends to have low rejection probability, the
test's power is a concern.  We'll present some power results,
simulating from \eqref{eq:1} with $c = 1$ or 2 subject to the
constraint that $\E_T \oosB > 0$.%
\footnote{Draws of $X$ and $Y$ with
  $\E_T \oosB > 0$ are very rare when $c=0$, so we do not present
  results for that value of $c$.} %
Figure~\ref{fig:ttest-power} plots
the power for the DMW test; since the other test statistics greatly
overreject, we do not present their power.  For $c=1$, the power is
never greater than nominal size and decreases to zero as $P/T$
increases for the overfit model.  For $c=2$ the power is better,
increasing with $P/T$ for a stretch and then decreasing as $P/T$ grows
beyond approximately 1/4 for the overfit model.  Larger values of $T$
give a higher peak and greater power overall, but the power still
falls to nearly zero if $P/T$ is too large (approximately 2/3 in our
simulations).  The power with the parsimonious model is typically
quite low but greater than nominal size for $c = 2$.

Both sets of simulations support our theoretical results.  The first
simulation confirms that the DMW OOS $t$-test is centered at $\E_R
\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
only when $P$ is small.  The second simulation confirms that the DMW
test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
when $P$ is small and that tests designed to test whether the
benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
and McCracken's (2007) OOS tests can reject by much more than their
nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
these simulations demonstrate that the restriction $P^2/T \to 0$ is
binding in practice, as the DMW test under-rejects and has very low
power when it is not satisfied.

@@

This section presents a study of equity premium predictability based
on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
of 18 different variables thought, based on previous research, to
predict the equity premium (calculated as the difference between the
return on the S\&P 500 index and the T-bill rate).%
\footnote{\citet{GoW:08} builds on previous research by \citet{BoH:99}
  and \cite{GoW:03}.} %
Their analysis has two notable features: they compare different
predictors across the same time periods and frequency as much as
possible, making the accuracy of these predictors directly comparable;
many of the papers that originally proposed these predictors used
different time periods, methods, or observational frequencies so their
results were not directly comparable. And Goyal and Welch compare
these predictors out-of-sample; many of the original studies found
in-sample evidence of equity premium predictability but did not look
at out-of-sample evidence.

@@

\citet{GoW:08} focus primarily on univariate regression models of the
form
\[
r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
\]
using OLS with a recursive window, where $r_{t+1}$ is the equity
premium and $x_{it}$ is one of the predictors listed in
Table~\ref{tab:equity}.%
\footnote{To make it easier to compare coefficients across variables
  and models, all of the regressors are studentized before our
  analysis and the equity premium is reported in basis points.} %
This focus is consistent with much of the rest of the literature. But
it is not clear that this approach---using a large number of
restricted models---is any more reliable than using a single, large
model. Very few papers in the equity-premium predictability literature
explicitly account for the multiplicity of model comparisons%
\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:13b} are
  exceptions.} %
and most widely-used statistics for multiple comparisons are
derived under the assumption that there is a finite number of
hypotheses or models (as is the case in \citealp{STW:99c},
\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
little theoretical evidence that they are any more reliable than a
regression model that encompasses all of the smaller models. Moreover,
since \citet{GoW:08} (along with most of the rest of the literature)
want to interpret these univariate regressions as meaningful
statements about the true relationships between the equity premium and
the regressors, omitted variable bias is a serious potential issue.

For example, Table~\ref{tab:gwinsample} presents two full-sample
coefficient estimates for each of the 12 predictors we consider.%
\footnote{For all of our full sample results, we studentize the
  regressors to make it easier to compare coefficient estimates and we
  express the equity premium in basis points.} %
The first column is the estimator of the coefficient on the listed
variable in the full regression,
\begin{equation*}
  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
\end{equation*}
and the third column is the $p$-value associated with a two-sided
$t$-test that the coefficient is zero in population. The second column
is the estimator of the coefficient from the univariate regression
\begin{equation*}
  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
\end{equation*}
and the fourth column is the $p$-value associated with its $t$-test.%
\footnote{All of the standard errors were calculated using a
  Newey-West kernel with two lags.} %
Some of the coefficient estimates agree, but some do not. The
coefficient estimate for the \emph{default yield spread}, for example,
is substantially and significantly negative in the full model ($-7.79$
with $p$-value $0.042$), but is near zero in the univariate regression
($0.79$ with $p$-value $0.720$). This pair of results implies that the
the default yield spread contains information about the equity premium
but is also correlated with other poor predictors, and that this
additional correlation adds noise to the univariate regression
and masks the true relationship. Similarly, \emph{net equity expansion}
is significant at 10\% in the univariate regression but not in the
full model ($p$-values of $0.060$ and $0.626$ respectively), which is
likely attributable to omitted variable bias. So there is merit to
studying a large model that includes all of the variables.

Results for the full sample estimates of these models are in
Table~\ref{tab:gwinsample}.%
\footnote{Calculations in this section are done in R \citep{Rde:10}
  using the \emph{lmtest} \citep{ZeH:02} and \emph{sandwich}
  \citep{Zei:04} packages. Tables and graphs were prepared with the
  \emph{dbframe} \citep{Cal:10b}, \emph{Hmsic} \citep{Har:10},
  \emph{tikzDevice} \citep{ShB:11:0.6.1}, and \emph{xtable}
  \citep{Dah:09} R packages as well as the \emph{booktabs}
  \citep{FeE:05} and \emph{TikZ and PGF} LaTeX packages
  \citep{Tan:10}}%
\footnote{We compare the test statistic to critical values from the
  $F$-distribution, which has been shown to be more reliable when
  there are many regressors \citep{Ana:12,Cal:11c}.} %
The last rows of the table list measures of the full-model fit.  The
$p$-value for the test of full model fit is very small (less than
0.01), indicating that the coefficients are nonzero in population and
at least one of these predictors is correlated with the equity
premium.%
\footnote{We have done additional analysis to try to identify which
  predictors were correlated with the equity premium, but none of the
  individual regressors were significant after correcting for
  multiplicity. The Bonferroni correction, for example, suggests that
  an individual $p$-value would need to be less than $0.10/12 \approx
  0.0083$ for its corresponding coefficient to be significant at the
  10\% level, but the smallest $p$-value is $0.035$. One can improve
  on the Bonferroni correction, but a comprehensive analysis is beyond
  the scope of this paper.} %
As we argue throughout the paper, this result does not imply that the
model will forecast well.

@@

In summary, we fail to reject the null that the benchmark prevailing
mean model is more accurate than the full model including all of
\citepos{GoW:08} predictors.  This result is consistent with Goyal and
Welch's original analysis.  Unlike Goyal and Welch, we attribute this
result, at least in part, to parameter uncertainty---the full sample
results indicate that there is a true predictive relationship between
some of these variables and the equity premium and the larger model
could predict better than the benchmark with enough data.%
\footnote{\citet{BWB:10} make a similar point about exchange rate
  models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
These also indicate that combination or shrinkage estimators of the
full model could significantly improve on the benchmark.%
\footnote{See \citet{RaZ:12} for a recent review of this
  literature.} %

@@

\begin{table}[tb]
  \begin{tabularx}{\linewidth}{XX}
    \toprule
    Category & Variable \\
    \midrule
    Stock market variables
    & Dividend to price ratio (log) \\
    & Earnings to price ratio (log) \\
    & Stock market variance \\
    & Book to market ratio \\
    & Net equity expansion \\
    & Percent equity issuing \\\\
    Interest rate variables
    & Treasury Bill rate (3 month) \\
    & Long term yield \\
    & Long term rate \\
    & Default return spread \\
    & Default yield spread \\
    & Inflation rate \\
    \bottomrule
  \end{tabularx}
  \caption{Variables used to predict the equity premium
    (Section~\ref{sec:empirics}).
    Please see Goyal and Welch's original paper \citep{GoW:08}
    for a detailed description of each variable.}
  \label{tab:equity}
\end{table}
\clearpage

>>>>

This section presents two simulations that investigate the accuracy of
our theory in small samples.
We do several Monte Carlo exercises. The first looks at wheather our
theoretical results for the OOS average are accuarate: whether or not
the OOS average is approximately normal, and whether it is centered on
$\E_R \oosA$, $\E_T \oosB$, or somewhere else entierely. The second
issue is whether or not the \oost\ test is \emph{useful} for
conducting inference about $\E_T \oosB$. Our theoretical results
suggest that it may not be, because we require $P^2/T \to 0$ for
inference about $\E_T \oosB$ to be valid. A highly related issue is
whether other statistics are useful for conducting inference about
$\E_T \oosB$---again, our theoretical results suggest that they are
not.

We use the same DGP for all of these simulations, and it is described
in the next subsection. Results are presented in the subsection after
that. Simulations were conducted in R \citep{Rde:10} using the
\emph{MASS} \citep{VeR:02}, \emph{Matrix} \citep{BM:13}, and
\emph{rlecuyer} \citep{SR:12} and graphs are produced using
\emph{Lattice} \citep{Sar:10}. In this paper, we present results for
the fixed window, but recursive window results are available in a
separate Appendix and are broadly similary.

@@

The Monte Carlo experiment is intentionally very simple so that we can
isolate the influence of the models' complexity.  In particular, we do
not include some features that are common in forecasting
environments---serial dependence, heteroskedasticity, and complicated
DGPs. The DGP we use is given by the equation
\begin{equation}\label{eq:6}
  y_t = x_t'\theta + \e_t,\quad \e_t \sim N(0,1),
  \quad t=1,\dots,T.
\end{equation}
The first element of $x_t$ is 1 and the remaining $K_2-1$ elements are
independent Standard Normal.  The benchmark model is
\begin{equation}
  \label{eq:1}
  y_{1t} = \sum_{j=1}^{K_1} x_{jt}\theta_j + \e_t
\end{equation}
and the alternative model is the DGP \eqref{eq:6}.  We let
$(K_1,K_2)$ equal either $(2,3)$ or $(T/20,T/10)$ to study our theory
in its intended application as well as for more parsimonious models.
We let $T$ equal 100, 250, or 500.  We also vary $\theta$, and do
so giving the benchmark and the alternative model comparable weight in
predicting $y_t$.  Specifically, we set
\begin{equation*}
  \theta_j =
\begin{cases} \frac{c}{\sqrt{K_1}} & j = 1,\dots,K_1 \\
\frac{c}{\sqrt{K_2 - K_1}} & j = K_1 + 1,\dots,K_2 \end{cases}
\end{equation*}
with $c$ equal to zero or one.  When $c$ is one, we're more likely to
draw values of $X$ and $Y$ that make the estimated larger model more
accurate than the benchmark, and when $c$ is zero we're unlikely to
draw such values of $X$ and $Y$.  For all of the studies, $L(e) =
e^2$.

To study the accuracy of our theoretical approximations, we first
estmate the coverage probabilities of OOS confidence intervals for
$\E_R \oosA$ and $\E_T \oosB$. For each draw of $X$ and $Y$, we
construct the one-sided OOS interval defined in
Theorem~\ref{res:oostest}:
\begin{equation*}
  [ \oosA - 1.28 \hat{\sigma}, \infty) \quad\text{with}\quad
  \sh^2 = \frac1P \sum_{t=R+1}^T (D_t - \oosA)^{2}
\end{equation*}
for $P = 10,\dots,2T/3$; we then calculate the percentage of
simulations where these intervals contain $\E_R \oosA$ and the
percentage that contain $\E_T \oosB$.  Since the data are i.i.d., both
of these quantities are easy to calculate (see
Section~\ref{sec:example}). For these calculations, we draw 2000
samples for each combination of the design parameters.

Our second set of results studies whether these different OOS and
in-sample statistics are valid for testing the null hypothesis
\begin{equation*}
  H_0:\quad E_T \oosB \leq 0,
\end{equation*}
namely that the benchmark model is expected to be more accurate in the
future than the alternative. Informally, we are interested in whether
the conditional probability
\begin{equation*}
  \Pr[\text{test rejects} \mid E_T \oosB \leq 0] \leq \alpha
\end{equation*}
where $\alpha$ is the nominal size of the test. If this inequality
does not hold, the test statistic is rejecting the benchmark model too
often.

We look at four different statistics---the full-sample $F$-test, the
DMW $t$-test, the OOS $t$-test using McCracken's (2007) critical
values,%
\footnote{These critical values are not published for $K_2-K_1>10$, so
  we do not report them for $K_2 = T/10$.} %
and Clark and West's (2006, 2007) Gaussian out-of-sample statistic.%
\footnote{Clark and West (2006, 2007) derive their statistic using the
  rolling window estimation scheme. Here we use the same statistic,
  but with a fixed window scheme. A supplemental appendix presents
  results for their statistic, using the recursive window.} %
For the $F$-test, we simply test whether the coefficients on the
larger model are nonzero.  For the out-of-sample tests, we conduct a
one-sided test of out-of-sample performance for every value of $P$ as
before. For each of these simulations, we discard draws from the DGP
that violate the null hypothesis $E_T \oosB \leq 0$ and then use the
remaining samples to calculate the conditional probability that each
test rejects. The simulations end when 2000 draws have been retained
for each choice of the design parameters.

@@

We discuss results for the confidence intervals first.
Figures~\ref{fig:interval-R} and~\ref{fig:interval-T} show the
coverage probability of these intervals as a function of $P$ for each
combination of $T$, $K_1$ and $K_2$, and $c$.  The nominal coverage is
90\%.  The gray horizontal line shows the intervals' nominal coverage
probability.  Each panel displays the coverage for a different choice
of design parameters.

Figure~\ref{fig:interval-R} gives the results for $\E_R \oosA$.  The
actual coverage is very close to the nominal coverage except when $P$
is very small.  The poor behavior for small $P$ is unsurprising, as it
simply means that the CLT is a poor approximation when the test sample
is small. The inteval for $T = 100$, $K = T/10$, and $c = 0$ is the
worst, with actual coverage near 85\% for most values of $P/T$. But
the others are much closer to nominal coverage, even for the
parsimonious models ($K_1=1$ and $K_2= 3$) where one might expect
the theoretical results to break down.

Figure~\ref{fig:interval-T} gives the results for $\E_T \oosB$.  In
columns 2 and 4---the overfit models---the coverage is near nominal
coverage for moderately small values of $P$.  As $P$ increases to
$2T/3$, the coverage increases above nominal size; near 100\% for some
DGPs.  With the parsimonious model, the coverage is near nominal
coverage for all $P$ for the one-sided interval with $c=1$, but only
for moderately small $P$ when $c=0$.

The behavior for $K_2 = T/10$ is exactly what our theory predicts.
When $P^2/T$ is small, the coverage is close to nominal levels.  The
behavior as $P$ increases, combined with the results for $\E_R \oosA$,
indicate that typically $\E_T \oosB \geq E_R \oosA$.  Since
\begin{equation*}
  E_{T} \oosB = E_{R} \oosA + (E_{T} \oosB - E_{R} \oosA),
\end{equation*}
and the interval is approximately centered at $\E_R \oosA$, the
difference $\E_{T} \oosB - E_{R} \oosA$ adds a substantial positive
quantity when $P^2/T$ is not near zero, increasing the coverage of the
one-sided interval.

We present the size simulations next, in
Figures~\ref{fig:ftest}--\ref{fig:ttest-power}.  For the OOS tests
We plot each OOS test's conditional rejection probability,
\begin{equation*}
  \Pr[\text{test rejects} \mid E_T \oosB \leq 0],
\end{equation*}
for each combination of $T$, $K_1$, $K_2$, and $c$ as a function of
$P$.  The $F$-test does not depend on $P$, so we calculate and
tabluate it's conditional rejection probability as a single value for
each combination of design parameters.

Table~\ref{fig:ftest} summarizes the simulation results for the
$F$-test. For $c = 0$, the estimated conditional rejection probability
is almost exactly equal to the test's nominal size (10\%), which is
unsurprising.  For $c = 0$, the $F$-test is exact; moreover, the
larger model will almost always be less accurate than the smaller one,
so conditioning on $\E_T \oosB \leq 0$ is almost unrestrictive.  When
$c$ increases, though, the $F$-test overrejects badly---rejecting at
roughly 50\% when $c = 1$ for the parsimonious model and from 70\% to
100\% for the overfit model. This agrees with our
Section~\ref{sec:insample} results and matches results seen in
empirical practice: the $F$-test rejects the benchmark with very high
probability, even though it is, by construction, more accurate than
the alternative model.

Figure~\ref{fig:ttest-size} presents the size estimates for the DMW
\oost\ test.  Again, different panels display results for different
combinations of the design parameters.  Each graph plots the rejection
probability against $P/T$.  For $K/T=10$, the rejection probability
falls as $P/T$ increases, from near nominal size when $P/T$ is small
to zero when $P/T$ is near $2/3$.  Moreover, the rejection probability
falls faster when $T$ is large, as our theory predicts.  When $K=3$,
the rejection probability stays closer to nominal size, but falls with
$P/T$ for $c=0$, under-rejecting by about 5pp when $P/T = 2/3$, and
rises with $P/T$ for $c=1$, overrejecting by about 10pp when
$P/T=2/3$.  For small $P$, the rejection probability is near 10\% for
all simulations (the farthest is $K=T/10$, $c=0$, where the rejection
probability is about 5\%; the other simulations are much closer).

@@

Results using \citepos{Mcc:07} critical values are presented in
Figure~\ref{fig:mccracken} and are similar to those using Clark and
West's test.  For $c=0$ the rejection probability is nearly the test's
nominal size.  For $c=1$, the rejection probability increases with
$P/T$, from close to the nominal size when $P/T$ is small to over 25\%
when $P/T = 2/3$.  Note that all of the simulations use the
parsimonious model.  McCracken's statistic overrejects here by
slightly less than Clark and West's, but still by a substantial
amount. Note that we are unable to plot results for McCracken's
statistic when $K/T = 10$, which is where the brakdown in Clark and
West's test is most pronounced.

Since the DMW test tends to have low rejection probability, the test's
power is a concern.  Figure~\ref{fig:ttest-power} power results for
the DMW test, simulating from \eqref{eq:1} with $c = 1$ or 2 subject
to the constraint that $\E_T \oosB > 0$.%
\footnote{Draws of $X$ and $Y$ with $\E_T \oosB > 0$ are very rare
  when $c=0$, so we do not present results for that value of $c$.} %
Since the other test statistics greatly overreject, we do not present
their power.  For $c=1$, the power is never greater than nominal size
and decreases to zero as $P/T$ increases for the overfit model.  For
$c=2$ the power is better, increasing with $P/T$ at first stretch and
then decreasing as $P/T$ grows beyond approximately 1/4 for the
overfit model.  Larger values of $T$ give a higher peak and greater
power overall, but the power still falls to nearly zero if $P/T$ is
too large (approximately 2/3 in our simulations).  The power with the
parsimonious model is typically quite low but greater than nominal
size for $c = 2$.

Both sets of simulations support our theoretical results.  The first
simulation confirms that the DMW OOS $t$-test is centered at $\E_R
\oosA$ for all choices of $P$ and $R$ and is centered on $\E_T \oosB$
only when $P$ is small.  The second simulation confirms that the DMW
test has correct size for the null hypothesis that $\E_T \oosB \leq 0$
when $P$ is small and that tests designed to test whether the
benchmark is true, like the $F$-test and Clark and West's (2006, 2007)
and McCracken's (2007) OOS tests can reject by much more than their
nominal size when testing the null $\E_T \oosB \leq 0$.  Moreover,
these simulations demonstrate that the restriction that $P$ be small
is binding in practice, as the DMW test under-rejects and has very low
power when $P$ is too large.

@@

This section presents a study of equity premium predictability based
on \citet{GoW:08}. Goyal and Welch conduct an out of sample analysis
of 18 different variables thought, based on previous research, to
predict the equity premium (calculated as the difference between the
return on the S\&P 500 index and the T-bill rate).%
\footnote{\citet{GoW:08} builds on previous research by \citet{BoH:99}
  and \cite{GoW:03}.} %
Their analysis has two notable features: Goyal and Welch compare different
predictors across the same time periods and frequency as much as
possible, making the accuracy of these predictors directly comparable;
many of the papers that originally proposed these predictors used
different time periods, methods, or observational frequencies so their
results were not directly comparable. And Goyal and Welch compare
these predictors out-of-sample; many of the original studies found
in-sample evidence of equity premium predictability but did not look
at out-of-sample evidence.

@@

\citet{GoW:08} focus primarily on univariate regression models of the
form
\[
r_{t+1} = \beta_0 + \beta_1 x_{it} + \e_{t+1}
\]
using OLS with a recursive window, where $r_{t+1}$ is the equity
premium and $x_{it}$ is one of the predictors listed in
Table~\ref{tab:equity}.
This focus is consistent with much of the rest of the literature. But
it is not clear that this approach---using a large number of
restricted models---is any more reliable than using a single, large
model. Very few papers in the equity-premium predictability literature
explicitly account for the multiplicity of model comparisons%
\footnote{\citet{RaW:06}, \citet{RaZ:12}, and \citet{Cal:13b} are
  exceptions.} %
and most widely-used statistics for multiple comparisons are
derived under the assumption that there is a finite number of
hypotheses or models (as is the case in \citealp{STW:99c},
\citealp{Whi:00}, \citealp{Han:05}, and \citealp{LeR:05}), so there is
little theoretical evidence that they are any more reliable than a
regression model that encompasses all of the smaller models. Moreover,
since \citet{GoW:08} (along with most of the rest of the literature)
want to interpret these univariate regressions as meaningful
statements about the true relationships between the equity premium and
the regressors, omitted variable bias is a serious potential issue.

For example, Table~\ref{tab:gwinsample} presents two full-sample
coefficient estimates for each of the 12 predictors we consider.%
\footnote{For all of our full sample results, we studentize the
  regressors to make it easier to compare coefficient estimates and we
  express the equity premium in basis points.} %
The first column is the estimator of the coefficient on the
variable in the full regression,
\begin{equation*}
  r_{t+1} = \beta_0 + \sum_{i=1}^{12} \beta_{i} x_{it} + \e_{t+1},
\end{equation*}
and the third column is the $p$-value associated with a two-sided
$t$-test that the coefficient is zero in population. The second column
is the estimator of the coefficient from the univariate regression
\begin{equation*}
  r_{t+1} = \alpha_i + \gamma_{i} x_{it} + \e_{t+1},
\end{equation*}
and the fourth column is the $p$-value associated with its $t$-test.%
\footnote{All of the standard errors were calculated using a
  Newey-West kernel with two lags.} %
Some of the coefficient estimates agree, but some do not. The
coefficient estimate for the \emph{default yield spread}, for example,
is substantially and significantly negative in the full model ($-7.79$
with $p$-value $0.042$), but is near zero in the univariate regression
($0.79$ with $p$-value $0.720$). This pair of results implies that the
the default yield spread contains information about the equity premium
but is also correlated with other poor predictors, and that this
additional correlation adds noise to the univariate regression
and masks the true relationship. Similarly, \emph{net equity expansion}
is significant at 10\% in the univariate regression but not in the
full model ($p$-values of $0.060$ and $0.626$ respectively), which is
likely attributable to omitted variable bias. So there is merit to
studying a large model that includes all of the variables.

Results for the full sample estimates of these models are in
Table~\ref{tab:gwinsample}.%
\footnote{Calculations in this section are done in R \citep{Rde:10}
  using the \emph{lmtest} \citep{ZeH:02} and \emph{sandwich}
  \citep{Zei:04} packages.}%
\footnote{We compare the test statistic to critical values from the
  $F$-distribution, which have been shown to be more reliable than
  Chi-squared critical values when there are many regressors
  \citep{Ana:12,Cal:11c}.} %
The last rows of the table list measures of the full-model fit.  The
$p$-value for the test of full model fit is very small (less than
0.01), indicating that some of the coefficients are nonzero in
population and at least one of these predictors is correlated with the
equity premium.%
\footnote{We have done additional analysis to try to identify which
  predictors were correlated with the equity premium, but none of the
  individual regressors were significant after correcting for
  multiplicity. The Bonferroni correction, for example, suggests that
  an individual $p$-value would need to be less than $0.10/12 \approx
  0.0083$ for its corresponding coefficient to be significant at the
  10\% level, but the smallest $p$-value is $0.035$. One can improve
  on the Bonferroni correction, of course, but a comprehensive
  analysis is beyond the scope of this paper.} %
As we argue throughout the paper, this result does not imply that the
model will forecast well.

@@

In summary, we fail to reject the null that the benchmark prevailing
mean model is more accurate than the full model including all of
\citepos{GoW:08} predictors.  This result is consistent with Goyal and
Welch's original analysis.  Unlike Goyal and Welch, we attribute this
result, at least in part, to parameter uncertainty---the full sample
results indicate that there is a true predictive relationship between
some of these variables and the equity premium and the larger model
could predict better than the benchmark with enough data.%
\footnote{\citet{BWB:10} make a similar point about exchange rate
  models, but see also \citet{Chi:10} and \citet{Gia:10}.} %
These also indicate that combination or shrinkage estimators of the
full model have the potential to significantly improve on the benchmark.%
\footnote{See \citet{RaZ:12} for a recent review of this
  literature.} %

@@

\begin{table}[tb]
  \begin{tabularx}{\linewidth}{XX}
    \toprule
    Category & Variable \\
    \midrule
    Stock market variables
    & Dividend to price ratio (log) \\
    & Earnings to price ratio (log) \\
    & Stock market variance \\
    & Book to market ratio \\
    & Net equity expansion \\
    & Percent equity issuing \\\\
    Interest rate variables
    & Treasury Bill rate (3 month) \\
    & Long term yield \\
    & Long term rate \\
    & Default return spread \\
    & Default yield spread \\
    & Inflation rate \\
    \bottomrule
  \end{tabularx}
  \caption{Variables used to predict the equity premium
    (Section~\ref{sec:empirics}).
    Please see Goyal and Welch's original paper \citep{GoW:08}
    for a detailed description of each variable.}
  \label{tab:equity}
\end{table}
